\section{Quick Start}
%###############################################################################

\subsection{Preparation}
%-------------------------------------------------------------------------------
Please see the Chapter 2.1 and 2.2 of ``SCALE USERS GUIDE''
as to the details of required system environment, library, and settings of environmental parameters.
Required libraries for SCALE-GM is same as SCALE-RM; HDF5, NetCDF, and MPI.

\subsection{Compile}
%-------------------------------------------------------------------------------
Please refer the Chapter 2.3.1 of ``SCALE USERS GUIDE'' for how to get the source code
and the Chapter 2.3.2 for the system environmental parameters.
Change directly to test case directly, for example,

\begin{verbatim}
  > cd ${TOP}/src
\end{verbatim}

\noindent Compile the program using make command.
\begin{verbatim}
  > make -j 4
\end{verbatim}
When the compile is finished correctly,
a "\verb|scale-gm|" is created in the directly of \verb|${ROOT}/bin|,
which is an executable binary of SCALE-GM.

\begin{itemize}
  \item[*] The number of -j option is a number of parallel compile processes.
   To reduce elapsed time of compile, you can specify the number
   as more than two. We recommend 2 $\sim$ 8 for the -j option.
\end{itemize}

\subsection{Run experiments}
%-------------------------------------------------------------------------------
\subsubsection{Test cases}

\noindent Inside the \${TOP}/test/case directory, you will find various test cases.
For example, the cases based on DCMIP2016 are shown in Table 1.

 \begin{table}[b]
 \begin{center}
 \caption{Corresponding test cases}
 \begin{tabularx}{150mm}{|l|X|} \hline
 \rowcolor[gray]{0.9} test case name in NICAM & test case type \\ \hline
  DCMIP2016-11 & moist baroclinic wave test (161)       \\ \hline
  DCMIP2016-12 & idealized tropical cyclone test (162)  \\ \hline
  DCMIP2016-13 & supercell test (163)                   \\ \hline
 \end{tabularx}
 \end{center}
 \end{table}


\subsubsection{How to run}

The script for job execution depends on the system.
SCALE-GM has a function, which produces scripts in consideration
of the difference of system environment.
Move to a directory of test case and then type
to create a job script and a script for post-processing;

 \begin{verbatim}
   > make jobshell
 \end{verbatim}

To run the model, type following command;

 \begin{verbatim}
   > make run
 \end{verbatim}

The test experiment will be started.

\subsection{Post process}
%-------------------------------------------------------------------------------
 After finish of test run, create the lat-lon grid data from
 the original icosahedral grid data.
 Before submit a job of post process, edit \verb|ico2ll_netcdf.sh|
 following your experimental settings.
 \begin{verbatim}
   > vi ico2ll_netcdf.sh

   [at Line 22]
   # User Settings
   # ---------------------------------------------------------------------

   glev=5          # g-level of original grid
   case=161        # test case number
   out_intev='day' # output interval (format: "1hr", "6hr", "day", "100s")
 \end{verbatim}

 \noindent If the job script is OK, submit a job to the machine.
 \begin{verbatim}
   sh ico2ll_netcdf.sh
 \end{verbatim}

% \begin{verbatim}
%   > bsub < ico2ll_netcdf.sh
% \end{verbatim}

 \noindent The netcdf format data such as "\verb|nicam.161.200.L30.interp_latlon.nc|"
 is created by an "ico2ll" post-process program.

