\section{Download and environmental settings} \label{sec:download}
%====================================================================================

The environment used in the explanation below is as follows:
\begin{itemize}
\item CPU: Intel Core i5 2410M 2 core /4 thread
\item Memory: DDR3-1333 4GB
\item OS: CentOS 6.6 x86-64, CentOS 7.1 x86-64, openSUSE 13.2 x86-64
\item GNU C/C++, FORTRAN compiler %(refer to Appendix \ref{achap:env_setting})
\end{itemize}

\subsubsection{Obtaining the source code} %\label{subsec:get_source_code}
%-----------------------------------------------------------------------------------
The source code for the latest release can be downloaded
from \url{https://scale.riken.jp/download/index.html}.\\
The directory \texttt{scale-{\version}/} can be seen when the tarball file of the source code is extracted.
\begin{alltt}
 $ tar -zxvf scale-{\version}.tar.gz
 $ ls ./scale-{\version}/
\end{alltt}

\subsubsection{Setting Makedef file and environment variables} \label{subsec:environment}
%-----------------------------------------------------------------------------------

\scalelib is compiled using a Makedef file
specified in the environment variable ``\verb|SCALE_SYS|.''
Several variations of the Makedef file corresponding to computer environment are prepared in the directory \texttt{scale-{\version}/sysdep/}.
Choose a Makedef file according to your environment.
Table \ref{tab:makedef} shows environments that Makedef files have supported. If there is no file for your environment, create a Makedif file by modifying any existing one.
For example,
if you use Linux x86-64 OS, a GNU compiler and OpenMPI,
"Makedef.Linux64-gnu-ompi" is apropriate.
An environment variable must also be specified as follows:
\begin{verbatim}
 $ export SCALE_SYS="Linux64-gnu-ompi"
\end{verbatim}
If the environment is always the same, it is convenient to explicitly describe the environmental variable in the environmental configuration file, such as \verb|.bashrc|.

\begin{table}[htb]
\begin{center}
\caption{Examples of environments and their corresponding Makedef files.}
\begin{tabularx}{150mm}{|l|l|X|l|} \hline
 \rowcolor[gray]{0.9} OS/Computer & Compiler & MPI & Makedef file \\ \hline
                 & gcc/gfortran & OpenMPI  & Makedef.Linux64-gnu-ompi \\ \cline{2-4}
 Linux OS x86-64 & icc/ifort    & IntelMPI & Makedef.Linux64-intel-impi \\ \hline
 Mac OS          & gcc/gfortran & OpenMPI  & Makedef.MacOSX-gnu-ompi \\ \hline
 Fujitsu FX700/FX1000 & fccpx/frtpx & mpiccpx/mpifrtpx & Makedef.FX700 \\ \hline
\end{tabularx}
\label{tab:makedef}
\end{center}
\end{table}


\scalelib requires \netcdf.
In the most cases, the pathes of \netcdf may be automatically found by using ``nc-config'' command.
If the paths cannot be found automatically, you should set the following paths.
You must set the environmental variables for \netcdf as follows:
\begin{verbatim}
 $ export SCALE_NETCDF_INCLUDE="-I/opt/netcdf/include"
 $ export SCALE_NETCDF_LIBS= \
        "-L/opt/hdf5/lib64 -L/opt/netcdf/lib64 -lnetcdff -lnetcdf -lhdf5_hl -lhdf5 -lm -lz"
\end{verbatim}


\section{Compile} \label{sec:compile}
%-----------------------------------------------------------------------------------

\subsubsection{Compile of \scalerm} %\label{subsec:compile}

Move to the \scalerm source directory
and compile it by executing the following command:
\begin{alltt}
 $ cd scale-{\version}/scale-rm/src
 $ make -j 4
\end{alltt}
The number of \verb|-j| option shows a number of parallel compile processes;
it is four-parallel in this example.
To reduce elapsed time of compile,
it is better to specify this option to execute parallel compilation.
Specify this number according to your environment.
When a compilation is successful,
the following three executable files are generated under the \texttt{scale-{\version}/bin} directory.
\begin{verbatim}
 scale-rm  scale-rm_init  scale-rm_pp
\end{verbatim}


\subsubsection{Compile of \scalegm} %\label{subsec:compile}

Move to the \scalegm source directory
and compile it by executing the following command:
\begin{alltt}
  $  cd scale-{\version}/scale-gm/src
  $  make -j 4
\end{alltt}

%The number of \verb|-j| option shows a number of parallel compile processes;
%it is four-parallel in this example.
%To reduce elapsed time of compile,
%it is better to use this option to execute parallel compilation.
%Specify this number according to your environment;
%we recommend the use of two $\sim$ eight processes.
When a compilation is successful,
the following three executable files are generated under the scale-{\version}/bin directory.

When a compilation is successful,
the following executable files are created in the \texttt{scale-{\version}/bin} directory.
``fio'' is original format based on binary with header information.
\begin{verbatim}
   scale-gm      (executable binary of \scalegm)
   gm_fio_cat    (cat command tool for fio format)
   gm_fio_dump   (dump tool for fio format file)
   gm_fio_ico2ll (convert tool from icosahedral grid data with fio format to LatLon grid data)
   gm_fio_sel    (sel command tool for fio format)
   gm_mkhgrid    (generation tool of icosahedral horizontal grid using spring grid)
   gm_mkllmap    (generation tool of LatLon horizontal grid)
   gm_mkmnginfo  (tool for creating management file of MPI process)
   gm_mkrawgrid  (generation tool of icosahedral horizontal grid)
   gm_mkvlayer   (generation tool of vertical grid)
\end{verbatim}


\subsubsection{Points to note}

\noindent If you want to compile them again, remove the created binary files by the following command:
\begin{verbatim}
 $ make clean
\end{verbatim}
Note that, the library already compiled is not deleted by this command.
When you recompile the files by changing the compilation environment and options, use the following command to remove all files created by compilation:
\begin{verbatim}
 $ make allclean
\end{verbatim}


In \scalelib, a compilation and an archive are conducted in directory \texttt{scale-{\version}/scalelib/}.
Object files are placed in a hidden directory called \verb|".lib"| under this directory when you carry out a compilation.

When you want to compile it in debug mode, compile it using \verb|"make -j 4 SCALE_DEBUG=T"|
(All the environment variables applied at compile time are listed in Table \ref{tab:env_var_list}).
If you want to change the compilation options in detail, edit \verb|Makedef.***| file.

\begin{table}[htb]
\begin{center}
\caption{List of environment variables applied at compile time}
\begin{tabularx}{150mm}{|l|X|} \hline
 \rowcolor[gray]{0.9} Environment variable & Description \\ \hline
 SCALE\_SYS               & Selection of system (required) \\ \hline
 SCALE\_DEBUG             & Use compile option for debug \\ \hline
 SCALE\_QUICKDEBUG        & Use compile option for quick debug (detect floating point error while maintaining speed-up option) \\ \hline
 SCALE\_USE\_SINGLEFP     & Use single precision floating-point number (for all sources) \\ \hline
 SCALE\_ENABLE\_OPENMP    & Enable to use OpenMP \\ \hline
 SCALE\_ENABLE\_OPENACC   & Enable to use OpenACC \\ \hline
 SCALE\_USE\_AGRESSIVEOPT & Conduct strong optimization (only for FX and intel, this can be a side effect) \\ \hline
 SCALE\_DISABLE\_INTELVEC & Suppress option for vectorization (only with Intel compiler) \\ \hline
 SCALE\_NETCDF\_INCLUDE   & Include path of NetCDF library \\ \hline
 SCALE\_NETCDF\_LIBS      & Directory path of NetCDF library and specifying libraries \\ \hline
 SCALE\_ENABLE\_PNETCDF   & Use Parallel NetCDF \\ \hline
 SCALE\_COMPAT\_NETCDF3   & Limit to NetCDF3-compatible features \\ \hline
 SCALE\_ENABLE\_MATHLIB   & Use numerical calculation library \\ \hline
 SCALE\_MATHLIB\_LIBS     & Directory path of numerical library and specifying libraries \\ \hline
 SCALE\_ENABLE\_PAPI      & Use Performance Application Programming Interface (PAPI) \\ \hline
 SCALE\_PAPI\_INCLUDE     & Include path of PAPI library \\ \hline
 SCALE\_PAPI\_LIBS        & Directory path of PAPI library and specifying libraries \\ \hline
 SCALE\_DISABLE\_LOCALBIN & Disable making local binary files in directory for test cases \\ \hline
 SCALE\_IGNORE\_SRCDEP    & Ignore dependency check at the compile time \\ \hline
 SCALE\_ENABLE\_SDM       & Use Super Droplet Method (SDM) model \\ \hline
\end{tabularx}
\label{tab:env_var_list}
\end{center}
\end{table}

