%Setting the physical process

\section{Turbulence scheme} \label{sec:basic_usel_turbulence}
%------------------------------------------------------

The turbulence scheme is specified in \nmitem{ATMOS_PHY_TB_TYPE} in \namelist{PARAM_ATMOS} in files \verb|init.conf| and \verb|run.conf|. The timing of the calling of the turbulence scheme is specified in \namelist{PARAM_TIME}. Refer to Section \ref{sec:timeintiv} for the detailed configuration of the calling timing.

\editboxtwo{
\verb|&PARAM_ATMOS  | & \\
\verb| ATMOS_PHY_TB_TYPE = "MYNN", | & ; Select the scheme shown in Table \ref{tab:nml_atm_tb}\\
\verb|/             | & \\
}
\begin{table}[h]
\begin{center}
  \caption{Choices of turbulence scheme}
  \label{tab:nml_atm_tb}
  \begin{tabularx}{150mm}{lXX} \hline
    \rowcolor[gray]{0.9}  Value & Description of scheme & Reference\\ \hline
      \verb|OFF|          & Do not calculate the turbulence process &  \\
      \verb|SMAGORINSKY|  & Smagorinsky—Lily-type sub-grid model & \citet{smagorinsky_1963,lilly_1962,Brown_etal_1994,Scotti_1993} \\
      \verb|D1980|        & Deardorff-type sub-grid model & \citet{Deardorff_1980} \\
      \verb|MYNN|         & MYNN Level 2.5 boundary scheme & \citet{my_1982,nakanishi_2004} \\
      \verb|HYBRID|       & Hybrid use of the boundary layer parameterization ans sub-grid scale turbulence model. Only the hybrid of \verb|SMAGORINSKY| and \verb|MYNN| is currently available.\\
    \hline
  \end{tabularx}
\end{center}
\end{table}

\verb|SMAGORINSKY| and \verb|D1980| are sub-grid scale turbulence models for Large-eddy simulations (LESs).
\verb|MYNN| is a boundary layer parameterization for Reynolds-Averaged Navier-Stokes equations (RANS).
\verb|HYBRID| is used for the following two purposes.
\begin{enumerate}
\item Simulations with inter-mediate resolution between LES and RANS (gray zone) \\
  The temporal tendencies by vertical mixing is calculated by a linear combination of those calculated by the LES turbulence model and RANS turbulence parameterization. The horizontal mixing is calculate by the LES turbulence model.
\item Horizontal eddy viscosity for RANS simulations \\
  The RANS turbulence parameterization is a scheme considering only vertical mixing.
  If you want to consider the horizontal eddy viscosity in RANS simulations,
  that becomes possible by using the \verb|HYBRID| scheme.
  The horizontal mixing is calculate by the LES turbulence model.
\end{enumerate}

In order to use the \verb|HYBRID| scheme for the horizontal eddy viscosity in RANS simulations, \nmitem{ATMOS_PHY_TB_SMG_horizontal} should be \verb|.true.| as follows:
\editboxtwo{
\verb|&PARAM_ATMOS_PHY_TB_SMG  | & \\
\verb| ATMOS_PHY_TB_SMG_horizontal = .true., | & \\
\verb|/             | & \\
}
